---
title: "CommVirusAnalysis"
author: "Vera Pfeiffer"
date: "7/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Community virus co-variance

This paper assesses the co-variance of bee viruses between honey bees and bumble bees.


```{r}
knitr::opts_chunk$set(echo = TRUE)

library(sp)
library(sf)
library(rgdal)
library(ggplot2)
library(ggmap)


setwd("~/Documents/BeeViruses/HBViruses")
Sites<-st_read("DataAnalysis/SitesPrj")
Sites$SiteCode

any(duplicated(Sites$SiteCode))
which(duplicated(Sites$SiteCode))
```

## Load HB and BB viruses data

```{r}
library(stringr)

setwd("~/Documents/BeeViruses/CommunityViruses")
CommVirus<-read.csv("DataAnalysis/CommViruses.csv")

Site<-strsplit(as.character(CommVirus$Code),"-")
SiteC<-as.character(lapply(Site, `[[`, 1))
CommVirus<-cbind(SiteC,CommVirus)

HBVirus<-CommVirus[which(CommVirus$BeeSp=="Apis_mellifera"),c("SiteC","Code","IAPV.158","DWV.269","SBV.342","ABPV.460","BQCV.536","CBPV.774")]

BBVirus<-CommVirus[which(CommVirus$BeeSp=="Bombus"),c("SiteC","Code","IAPV.158","DWV.269","SBV.342","ABPV.460","BQCV.536","CBPV.774")]

BeeVirus<-CommVirus[which(CommVirus$BeeSp=="Bombus"|CommVirus$BeeSp=="Apis_mellifera"),c("SiteC","Code","IAPV.158","DWV.269","SBV.342","ABPV.460","BQCV.536","CBPV.774")]
```


Here are the number of positive tests for each virus, total,

```{r, echo=TRUE}
sum(HBVirus$IAPV.158, na.rm = TRUE) #6
sum(HBVirus$DWV.269, na.rm = TRUE) #92
sum(HBVirus$SBV.342, na.rm = TRUE) #65
sum(HBVirus$ABPV.460, na.rm = TRUE) #1
sum(HBVirus$BQCV.536, na.rm = TRUE) #97
sum(HBVirus$CBPV.774, na.rm = TRUE) #20/257 = 

sum(BBVirus$IAPV.158, na.rm = TRUE) #34
sum(BBVirus$DWV.269, na.rm = TRUE) #40
sum(BBVirus$SBV.342, na.rm = TRUE) #0
sum(BBVirus$ABPV.460, na.rm = TRUE) #0
sum(BBVirus$BQCV.536, na.rm = TRUE) #27
sum(BBVirus$CBPV.774, na.rm = TRUE) #2/809 =

```

And the number of positive tests by site


```{r, echo=TRUE}
library(dplyr)
HBVirusR<-HBVirus
HBVirusR[is.na(HBVirus)] = 0
HBVirusCol<- HBVirusR %>%
  group_by(SiteC) %>%
  summarise(IAPV.158 = max(IAPV.158), DWV.269 = max(DWV.269), SBV.342 = max(SBV.342), ABPV.460 = max(ABPV.460), BQCV.536 = max(BQCV.536), CBPV.774 = max(CBPV.774), na.rm=TRUE)

HBVirusCol2 <- HBVirusR %>% 
  group_by(SiteC) %>% 
  summarise(HBIAPV.158p = sum(IAPV.158), HBIAPV.158n = length(IAPV.158)-sum(IAPV.158), HBIAPV.158Prop = sum(IAPV.158)/(length(IAPV.158)), HBDWV.269p = sum(DWV.269), HBDWV.269n = length(DWV.269)-sum(DWV.269), HBDWV.269Prop = sum(DWV.269)/(length(DWV.269)), HBSBV.342p = sum(SBV.342), HBSBV.342n = length(SBV.342)-sum(SBV.342), HBSBV.342Prop = sum(SBV.342)/(length(SBV.342)), HBABPV.460p = sum(ABPV.460), HBABPV.460n = length(ABPV.460)-sum(ABPV.460), HBABPV.460Prop = sum(ABPV.460)/(length(ABPV.460)), HBBQCV.536p = sum(BQCV.536), HBBQCV.536n = length(BQCV.536)-sum(BQCV.536), HBBQCV.536Prop = sum(BQCV.536)/(length(BQCV.536)), HBCBPV.774p = sum(CBPV.774), HBCBPV.774n = length(CBPV.774)-sum(CBPV.774), HBCBPV.774Prop = sum(CBPV.774)/(length(CBPV.774)), na.rm=TRUE)


BBVirusR<-BBVirus
BBVirusR[is.na(BBVirus)] = 0
BBVirusCol<- BBVirusR %>%
  group_by(SiteC) %>%
  summarise(IAPV.158 = max(IAPV.158), DWV.269 = max(DWV.269), SBV.342 = max(SBV.342), ABPV.460 = max(ABPV.460), BQCV.536 = max(BQCV.536), CBPV.774 = max(CBPV.774), na.rm=TRUE)

BBVirusCol2 <- BBVirusR %>% 
  group_by(SiteC) %>% 
  summarise(IAPV.158p = sum(IAPV.158), IAPV.158n = length(IAPV.158)-sum(IAPV.158), IAPV.158Prop = sum(IAPV.158)/(length(IAPV.158)), DWV.269p = sum(DWV.269), DWV.269n = length(DWV.269)-sum(DWV.269), DWV.269Prop = sum(DWV.269)/(length(DWV.269)), SBV.342p = sum(SBV.342), SBV.342n = length(SBV.342)-sum(SBV.342), SBV.342Prop = sum(SBV.342)/(length(SBV.342)), ABPV.460p = sum(ABPV.460), ABPV.460n = length(ABPV.460)-sum(ABPV.460), ABPV.460Prop = sum(ABPV.460)/(length(ABPV.460)), BQCV.536p = sum(BQCV.536), BQCV.536n = length(BQCV.536)-sum(BQCV.536), BQCV.536Prop = sum(BQCV.536)/(length(BQCV.536)), CBPV.774p = sum(CBPV.774), CBPV.774n = length(CBPV.774)-sum(CBPV.774), CBPV.774Prop = sum(CBPV.774)/(length(CBPV.774)), na.rm=TRUE)


sum(HBVirusCol$IAPV.158, na.rm = TRUE) #6
sum(HBVirusCol$DWV.269, na.rm = TRUE) #47
sum(HBVirusCol$SBV.342, na.rm = TRUE) #36
sum(HBVirusCol$ABPV.460, na.rm = TRUE) #1
sum(HBVirusCol$BQCV.536, na.rm = TRUE) #52
sum(HBVirusCol$CBPV.774, na.rm = TRUE) #12/86

sum(BBVirusCol$IAPV.158, na.rm = TRUE) #12
sum(BBVirusCol$DWV.269, na.rm = TRUE) #9
sum(BBVirusCol$SBV.342, na.rm = TRUE) #0
sum(BBVirusCol$ABPV.460, na.rm = TRUE) #0
sum(BBVirusCol$BQCV.536, na.rm = TRUE) #12
sum(BBVirusCol$CBPV.774, na.rm = TRUE) #2/87


#names(BBVirusCol)<-c("SiteC","BB.IAPV.158","BB.DWV.269","BB.SBV.342","BB.ABPV.460","BB.BQCV.536","BB.CBPV.774","na.rm")

#names(HBVirusCol)<-c("SiteC","HB.IAPV.158","HB.DWV.269","HB.SBV.342","HB.ABPV.460","HB.BQCV.536","HB.CBPV.774","na.rm")

CommVirData<- HBVirusCol2 %>% full_join(BBVirusCol2)
#CommVirData<-CommVirData[,-8]
```

To check the correlation between HB and BBs for each virus overall...
```{r, echo=FALSE}
library("Hmisc")

HBBBProps<-CommVirData[,c(4,7,10,13,16,19,23,26,29,32,35,38)]
rcorr(as.matrix(HBBBProps), type = c("pearson"))
```


To check the correlation between HB and BBs for each virus in urban and commercial sites...
```{r, echo=FALSE}
#UrbanSites <- allbeevirusPts$SiteCode[allbeevirusPts$Landscape=="Urban"]
#UrbHBBBProps <- CommVirData[!CommVirData$SiteC %in% UrbanSites, ]
#UrbHBBBProps <- CommVirData[CommVirData$SiteC %in% UrbanSites, c(4,7,10,13,16,19,23,26,29,32,35,38)]
#rcorr(as.matrix(UrbHBBBProps), type = c("pearson"))

#CommSites <- allbeevirusPts$SiteCode[allbeevirusPts$Apiary=="Commercial"]
#CommHBBBProps <- CommVirData[CommVirData$SiteC %in% CommSites, c(4,7,10,13,16,19,23,26,29,32,35,38)]
#rcorr(as.matrix(CommHBBBProps), type = c("pearson"))
#CommVirData
```

Map
```{r, echo=FALSE}

#install.packages("viridis")  # Install
library("viridis") 
library(ggmap)

all(CommVirData$SiteC %in% Sites$SiteCode)

# Merge HBSites and HBVirusR: beevirusPts
allbeevirusPts<-merge(Sites,BBreg, by.x="SiteCode", by.y="SiteCode")
plot(allbeevirusPts)

map <- get_stamenmap(c(left = -124.9, bottom = 45.2, right = -115.5, top = 48.9), zoom = 6, maptype = c("toner-lite"))
ggmap(map) +
  geom_point(aes(Longitude, Latitude, color = RegionalDensity), data = BBvirusPts2)
ggmap(map) +
  geom_point(aes(Longitude, Latitude), data = BBvirusPts2)


#BB_IAPVmap
ggmap(map) +
  geom_point(aes(Longitude, Latitude, color = IAPV.158Prop), data = allbeevirusPts)

#BB_DWVmap
ggmap(map) +
  geom_point(aes(Longitude, Latitude, color = DWV.269Prop), data = allbeevirusPts)

#BB_BQCVmap
ggmap(map) +
  geom_point(aes(Longitude, Latitude, color = BQCV.536Prop), data = allbeevirusPts)


#HB_IAPVmap
ggmap(map) +
  geom_point(aes(Longitude, Latitude, color = HBIAPV.158Prop), data = allbeevirusPts)

#HB_DWVmap
ggmap(map) +
  geom_point(aes(Longitude, Latitude, color = HBDWV.269Prop), data = allbeevirusPts)

#HB_BQCVmap
ggmap(map) +
  geom_point(aes(Longitude, Latitude, color = HBBQCV.536Prop), data = allbeevirusPts)

```

To check the correlation between HB and BBs for each virus by landscape subset...
```{r, echo=FALSE}
library("Hmisc")

UrbanVirData<-allbeevirusPts[which(allbeevirusPts$Landscape=="Urban"),]
UrbanVirMat<-as.data.frame(UrbanVirData[38:49])
rcorr(as.matrix(UrbanVirMat[,1:12]), type = c("pearson"))


RuralPollVirData<-allbeevirusPts[which(allbeevirusPts$Landscape=="Agricultural"|allbeevirusPts$Ecotype=="Steppe"),]
RuralPollVirData<-RuralPollVirData[which(RuralPollVirData$Apiary=="Commercial"),]
RuralPollVirMat<-as.data.frame(RuralPollVirData[38:49])
rcorr(as.matrix(RuralPollVirMat[,1:12]), type = c("pearson"))

```



logistic regression to predict BB viruses...
```{r, echo=FALSE}
head(BBVirusR)
names(BBVirusR)<-c("SiteC","Code","BB.IAPV.158","BB.DWV.269","BB.SBV.342","BB.ABPV.460","BB.BQCV.536","BB.CBPV.774")
#BBvirusPts<-merge(Sites,BBVirusCol2, by.x="SiteCode", by.y="SiteC")
#BBvirusPts2<-BBvirusPts[-is.na(BBvirusPts$IAPV.158Prop),]
#BBvirusPts2<-BBvirusPts

BBvirusPts<-merge(Sites,CommVirData, by.x="SiteCode", by.y="SiteC")
#BBvirusPts2<-allbeevirusPts[-is.na(allbeevirusPts$IAPV.158Prop),]
BBvirusPts2<-BBvirusPts


BBvirusPts2$Urban<-0
BBvirusPts2$Urban[which(BBvirusPts2$Landscape=="Urban")]<-1

BBvirusPts2$Commercial<-0
BBvirusPts2$Commercial[which(BBvirusPts2$Apiary=="Commercial")]<-1

BBvirusPts2$Forest<-0
BBvirusPts2$Forest[which(BBvirusPts2$Ecotype=="Forest")]<-1

library(aod)
#BBreg<-BBvirusPts2[,c(1,40,43,51,56,57,58,59,60,61,68,69,70,75,76,77)]
BBreg<-BBvirusPts2[,c(1,38:74,76:78)]
#contingency table to check for NAs
xtabs(~IAPV.158Prop + Urban, data = BBreg)
xtabs(~DWV.269Prop + Commercial, data = BBreg)
xtabs(~BQCV.536Prop + Forest, data = BBreg)



library(tidyr)
BBregNA<-BBreg %>% drop_na() #101 goes to 71

IAPVpos<-BBregNA$HBIAPV.158Prop[which(BBregNA$HBIAPV.158Prop>0)]
DWVpos<-BBregNA$HBDWV.269Prop[which(BBregNA$HBDWV.269Prop>0)]
BQCVpos<-BBregNA$HBBQCV.536Prop[which(BBregNA$HBBQCV.536Prop>0)]

InfectionRate<-c(BQCVpos,DWVpos,IAPVpos)
Virus<-c(rep("BQCV",length(BQCVpos)),rep("DWV",length(DWVpos)),rep("IAPV",length(IAPVpos)))

inf<-cbind(Virus,InfectionRate)


# Fit and plot regression for IAPV

myIAPVlogit <- glm(cbind(IAPV.158p,IAPV.158n) ~ HBIAPV.158Prop + Urban + Commercial, data = BBregNA, family = "binomial", na.action = na.fail)
summary(myIAPVlogit)
exp(cbind(OR = coef(myIAPVlogit), confint(myIAPVlogit)))

LogORmat<-cbind(OR = coefTable(myIAPVlogit)[,1], lse = coefTable(myIAPVlogit)[,1]-coefTable(myIAPVlogit)[,2], hse = coefTable(myIAPVlogit)[,1]+coefTable(myIAPVlogit)[,2])
LogORmat<-as.data.frame(LogORmat)
LogORmat$names<-row.names(LogORmat)
names(LogORmat)<-c("logOdds","lse","hse","names")

LogORmat %>%
  ggplot(aes(x=names, y=logOdds)) + 
    geom_col() +
    geom_errorbar(aes(ymin=lse, ymax=hse, width=.1))


library(MuMIn)
IAPVavg <- dredge(myIAPVlogit, rank = "AICc")
ma <- model.avg(IAPVavg, subset = cumsum(weight) <= .95)
bw <- Weights(ma)
LogORmat<-cbind(OR = coef(ma), confint(ma))
LogORmat<-as.data.frame(LogORmat)
LogORmat$names<-c("Intercept", "Urban", "HBIAPV", "Commercial")
names(LogORmat)<-c("logOdds","lse","hse","names")

# Standard error of the mean
LogORmat %>%
  arrange(names) %>%    # First sort by val. This sorts the dataframe but NOT the factor levels
  mutate(names=factor(names, levels=names)) %>%   # This trick update the factor levels
  ggplot(aes(x=names, y=logOdds)) + 
    geom_col() +
    geom_errorbar(aes(ymin=lse, ymax=hse, width=.1))

                  


# Fit and plot regression for DWV
myDWVlogit <- glm(cbind(DWV.269p,DWV.269n) ~ HBDWV.269Prop + Urban + Commercial, data = BBregNA, family = "binomial", na.action = na.fail)
summary(myDWVlogit)
ORMat<-exp(cbind(OR = coef(myDWVlogit), confint(myDWVlogit)))

LogORmat<-cbind(OR = coefTable(myDWVlogit)[,1], lse = coefTable(myDWVlogit)[,1]-coefTable(myDWVlogit)[,2], hse = coefTable(myDWVlogit)[,1]+coefTable(myDWVlogit)[,2])
LogORmat<-as.data.frame(LogORmat)
LogORmat$names<-row.names(LogORmat)
names(LogORmat)<-c("logOdds","lse","hse","names")

LogORmat %>%
  ggplot(aes(x=names, y=logOdds)) + 
    geom_col() +
    geom_errorbar(aes(ymin=lse, ymax=hse, width=.1))

library(MuMIn)
DWVavg <- dredge(myDWVlogit, rank = "AICc")
ma <- model.avg(DWVavg, subset = cumsum(weight) <= .95)
bw <- Weights(ma)
LogORmat<-cbind(OR = coef(ma), confint(ma))
LogORmat<-as.data.frame(LogORmat)
LogORmat$names<-c("Intercept", "Urban", "Commercial", "HBDWV")
names(LogORmat)<-c("logOdds","lse","hse","names")

# Standard error of the mean
LogORmat %>%
  ggplot(aes(x=names, y=logOdds)) + 
    geom_col() +
    geom_errorbar(aes(ymin=lse, ymax=hse, width=.1))
                  





# Fit and plot regression for BQCV
myBQCVlogit <- glm(cbind(BQCV.536p,BQCV.536n) ~ HBBQCV.536Prop + Urban + Commercial, data = BBregNA, family = "binomial", na.action = na.fail)
summary(myBQCVlogit)
ORMat<-exp(cbind(OR = coef(myBQCVlogit), confint(myBQCVlogit)))

LogORmat<-cbind(OR = coefTable(myBQCVlogit)[,1], lse = coefTable(myBQCVlogit)[,1]-coefTable(myBQCVlogit)[,2], hse = coefTable(myBQCVlogit)[,1]+coefTable(myBQCVlogit)[,2])
LogORmat<-as.data.frame(LogORmat)
LogORmat$names<-row.names(LogORmat)
names(LogORmat)<-c("logOdds","lse","hse","names")

LogORmat %>%
  ggplot(aes(x=names, y=logOdds)) + 
    geom_col() +
    geom_errorbar(aes(ymin=lse, ymax=hse, width=.1))

library(MuMIn)
BQCVavg <- dredge(myBQCVlogit, rank = "AICc")
ma <- model.avg(BQCVavg, subset = cumsum(weight) <= .95)
bw <- Weights(ma)
LogORmat<-cbind(OR = coef(ma), confint(ma))
LogORmat<-as.data.frame(LogORmat)
LogORmat$names<-c("Intercept", "HBBQCV", "Commercial", "Urban")
names(LogORmat)<-c("logOdds","lse","hse","names")

# Standard error of the mean
LogORmat %>%
  ggplot(aes(x=names, y=logOdds)) + 
    geom_col() +
    geom_errorbar(aes(ymin=lse, ymax=hse, width=.1))
     




                  
#Make new data
pd = data.frame(HBIAPV.158Prop = c(rep(0,4), rep(0.33,4), rep(0.66,4), rep(1,4)), Urban = rep(c(0,1),8), Commercial = rep(c(0,0,1,1),4))

# use type = "response" for probability-scale predictions    
preds = predict(myIAPVlogit, newdata = pd, type = "response", se.fit = TRUE)
pd$fit = preds$fit
pd$se = preds$se.fit

ggplot(BBreg, aes(x = Urban, y = IAPV.158Prop)) +
  geom_point(position = position_jitter(width = 0.05, height = 0.05)) +
  geom_ribbon(data = pd, aes(y = fit, ymin = fit - 1.96 * se, ymax = fit + 1.96 * se),
              fill = "blue", alpha = 0.3) +
  geom_line(data = pd, aes(y = fit)) 








#regression for BQCV co-occurance
BBreg$BQCV_Co<-0
BBreg$BQCV_Co[which(BBreg$BQCV.536Prop>0 & BBreg$HBBQCV.536Prop>0)]<-1

length(unique(BBreg$SiteCode))
survey<-read.csv("DataAnalysis/ApiarySurvey.csv")
BHreg<-merge(BBreg,survey[,c(3,7,11,17,18)], by.x="SiteCode", by.y="SiteCode")

# Fit and plot regression for BQCV
CoBQCVlogit <- glm(BHreg$BQCV_Co ~ Urban + Commercial+ ActiveHives + RegionalDensity , data = BHreg, family = "binomial")
summary(CoBQCVlogit)
exp(cbind(OR = coef(CoBQCVlogit), confint(CoBQCVlogit)))

CoBQCVlogit <- glm(BHreg$BQCV_Co ~ RegionalDensity , data = BHreg, family = "binomial")
summary(CoBQCVlogit)
ORMat<-exp(cbind(OR = coef(CoBQCVlogit), confint(CoBQCVlogit)))

#Model averaging
library(tidyr)
library(dplyr)
BHregSub<-cbind(Urban = BHreg$Urban,Commercial = BHreg$Commercial, ActiveHives = BHreg$ActiveHives, RegionalDensity = BHreg$RegionalDensity, BQCV_Co = BHreg$BQCV_Co)

BHregNA<-BHregSub %>% drop_na()
CoBQCVlogit <- glm(BHreg$BQCV_Co ~ Urban + Commercial+ ActiveHives + RegionalDensity , data = BHregNA, family = "binomial", na.action = na.fail) 
summary(CoBQCVlogit)
exp(cbind(OR = coef(CoBQCVlogit), confint(CoBQCVlogit)))


library(MuMIn)
CoBQavg <- dredge(CoBQCVlogit, rank = "AICc")
ma <- model.avg(CoBQavg)
bw <- Importance(CoBQavg)
ORmat<-exp(cbind(OR = coef(ma), confint(ma)))
ORmat<-as.data.frame(ORmat)
ORmat$names<-c("Intercept", "RegionalDensity", "Urban", "ActiveHives", "Commercial")
names(ORmat)<-c("OR","lse","hse","names")

IAPVavg <- dredge(myIAPVlogit, rank = "AICc")
ma <- model.avg(IAPVavg)
bw <- Weights(ma)
ORmat<-exp(cbind(OR = coef(ma), confint(ma)))
ORmat<-as.data.frame(ORmat)
ORmat$names<-c("Intercept", "Urban", "HBIAPV", "Commercial")
names(ORmat)<-c("OR","lse","hse","names")

#Make new data
pd = data.frame(BQCV_Co = c(rep(0,4), rep(1,4)), RegionalDensity = rep(c(1,2,3,4),2))

# use type = "response" for probability-scale predictions    
preds = predict(CoBQCVlogit, newdata = pd, type = "response", se.fit = TRUE)
pd$fit = preds$fit
pd$se = preds$se.fit

ggplot(BHreg, aes(x = RegionalDensity, y = BQCV_Co)) +
         ylab("Co-occurrence") +
  xlab("Regional density of honey bee apiaries") +
  geom_point(position = position_jitter(width = 0.05, height = 0.05)) +
  geom_ribbon(data = pd, aes(y = fit, ymin = fit - 1.96 * se, ymax = fit + 1.96 * se),
              fill = "blue", alpha = 0.3) +
  geom_line(data = pd, aes(y = fit)) 



ggplot(newdata3, aes(x = gre, y = PredictedProb)) + geom_ribbon(aes(ymin = LL,
    ymax = UL, fill = rank), alpha = 0.2) + geom_line(aes(colour = rank),
    size = 1)


mylogit <- glm(BB.DWV.269 ~ Urban + Commercial, data = BBreg, family = "binomial")
exp(cbind(OR = coef(mylogit), confint(mylogit)))

mylogit <- glm(BB.IAPV.158 ~ Urban + Commercial, data = BBreg, family = "binomial")
exp(cbind(OR = coef(mylogit), confint(mylogit)))


```


Add some variability to BB points to prepare for spatial regression
```{r, echo=FALSE}
coords<-st_coordinates(BBvirusPts$geometry)

BBvirusPts$Xcoord<-coords[,1]
Xrerr<-rnorm(805,0,100)
BBvirusPts$Xcoord<-BBvirusPts$Xcoord+Xrerr

BBvirusPts$Ycoord<-coords[,2]
Yrerr<-rnorm(805,0,100)
BBvirusPts$Ycoord<-BBvirusPts$Ycoord+Yrerr

coords[,1]<-BBvirusPts$Xcoord
coords[,2]<-BBvirusPts$Ycoord

knn<-knearneigh(coords,50)
nb<-knn2nb(knn)

```


Spatial regression to predict BB viruses...
Method follows https://www.youtube.com/watch?v=b3HtV2Mhmvk
```{r, echo=FALSE}
head(BBVirusR)

install.packages("spdep")
install.packages("rgdal")
install.packages("rgeos")

library("spdep")
library("rgdal")
library("rgeos")


nb.listw=nb2listw(nb)

#define our regression equation
reg.eq1= BBvirusPts$BB.IAPV.158~BBvirusPts$Commercial+BBvirusPts$Urban

options(scipen=7)

reg1 = glm(reg.eq1,data=BBvirusPts)
summary(reg1)

#Morans correlation test designed for regression residuals - you give it a spatial relations matrix of choice
lm.morantest(reg1,nb.listw)

#La grange multiplier test
#lm.LMtests(reg1,nb.listw,test="all")
lm.LMtests(reg1,nb.listw,test=c("LMerr","LMlag", "RLMerr", "RLMlag", "SARMA"))

#"LMerr" - testing to see how much our model would improve if we ran a spatial error model - the p value suggests a spatial error model would improve the fit.

#"LMlag" - testing to see how much our model would improve if we ran a spatial lag model - the p value suggests a spatial lag model would improve the fit.

#"RLMerr" - this is a Robust la grange multiplier tests, seeing if a error model would improve the fit, but trying to filter out some of the false positives - because a lag model can be a false positive for an error, and vice versa because there are some similarities in their fitting

#"RLMlag" - compare the p value with the one above to see which one we should run

#"SARMA" - R is not capable of running a SARMA model





#p=rho, T=theta, L=lambda
#SAR Spatial lag (autoregressive) model y=pWy + xB + E
reg3 = lagsarlm(reg.eq1, data=BBvirusPts, nb.listw)

#Anything with a Lag Y in it: You cannot interpret betas as marginal effects
#You must use the impacts command
impacts(reg3, listw=nb.listw)
#The direct effect is the when we increase our impact by the marginal value, while the indirect impact is the effect if all our neighbors increased their behaviour, or the total effect of our increase on all our neighbors

summary(impacts(reg3, listw=nb.listw, R=500),zstats=TRUE) #Add zstats,pvalues

#Also,

#Spatial error model
reg4=errorsarlm(reg.eq1.data=BBvirusPts, nb.listw)

#Lambda value - that tells us the effect of a stochastic shock to our neighbors - you can use the normal estimates, the effects are only to the residuals

#Spatial Hausman test (Pace and LeSage)
#Original 1978 - Hausman - if you have two choices between models including fixed effects or not... the problem is if you don't include the fixed effects it will cause bias. If you leave out the fixed effects

#Comparing OLS to spatial error model
#since the structure of the spatial noise is only in the #residuals - it's a spatial autocorrelation issue - it should #not bias the parameters if you estimate with OLS, it's just #that the spatial errors will be corrected in the spatial #error model. If they are very different - it suggests that #neither model is correct, and there could be spatial #dependence that is not captured.

Hausman.test(reg4)
#if significant, OLS and spatial error are probably both wrong.

```

Spatial autocorrelation
```{r, echo=FALSE}

library(ncf)
ncf.cor <- correlog(coords[,1], coords[,2], BBvirusPts$BB.IAPV.158, increment=500, resamp=100)
```


